---
title: "Lab 1 - Hello R"
author: "Annie Hou"
date: "01/25/2024"
output: html_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

```
datasaurus_dozen %>%
  count(dataset) %>%
  print()
```

Using the code above, we could find there are 13 rows and 2 columns. The variables are dataset, x, and y.

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First, plot the data in the dino dataset. Now, we plot `y` vs. `x` for the star dataset. 

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

Now the correlation equals to -0.0630. Notice that the correlation increases a little compared to the previous dino data but still remain negative, which means a less strong negative linear correlation.

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.
To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.
